Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-28 paper/comoving-followup.tex
uncomment figures

\author{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}
\affiliation{To whom correspondence should be addressed:
             \texttt{adrn@astro.princeton.edu}}

@@

@@

\keywords{
    TODO
}

@@

% \begin{figure}[htbp]
%   \begin{center}
%     \includegraphics[width=\linewidth]{mcmc_corner.pdf}
%   \end{center}
%   \caption{%
%     \todo{Some summary plots about the MCMC fits...}
%     Small uncertainty in centroid = 2 km/s velocity precision here.
%     \label{fig:Halpha-mcmc-corner}}
% \end{figure}

% \begin{figure}[htbp]
%   \begin{center}
%     \includegraphics[width=\linewidth]{mcmc_example_fit.pdf}
%   \end{center}
%   \caption{%
%     Top shows background linear model + Voigt line model.
%     \label{fig:Halpha-mcmc-fit}}
% \end{figure}

>>>>

\author{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}

@@

\correspondingauthor{Adrian M. Price-Whelan}
\email{adrn@astro.princeton.edu}

@@

\keywords{
    binaries: spectroscopic
    ---
    methods: observational
    ---
    techniques: radial velocities
    ---
    catalogs
    ---
    stars: formation
}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_corner.pdf}
  \end{center}
  \caption{%
    \todo{Some summary plots about the MCMC fits...}
    Small uncertainty in centroid = 2 km/s velocity precision here.
    \label{fig:Halpha-mcmc-corner}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_example_fit.pdf}
  \end{center}
  \caption{%
    Top shows background linear model + Voigt line model.
    \label{fig:Halpha-mcmc-fit}}
\end{figure}
